### 2019-07-05 manuscript.tex
Comments on Main part of intro

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15, with another 15 millions girls at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade if the trends continue \cite{KhosBane17, UNIC16}.  FGC is also known as female genital mutilation and female circumcision.  As adapted by Tostan \cite{Tost15}, cutting is preferred over circumcision without diminishing or excusing the negative impact of the practice because it implies a degree of self-awareness and is considered less judgmental  \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

The commonly shared position for the practice of FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update}.  The progress is hindered due to the complicated history of the very practice \cite{BergDeni12, Cami16}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, and by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values and norms attached to FGC practice is essential to comprehend the persistence of FGC practice \cite{}.  Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in comprehending,  intervening or eradicating the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} \cfonly{more cites}.

Social norm is often used to understand behavioural pattern of FGC \cfonly{more cite{BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17, Youn02} (to confirm)}.  Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.  Convention theory, a widely inferred approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC is also viewed as a social capital for inclusion and exclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.

Although convention theory was well deliberated and applied and showed a larger effect on FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}),  it was not without challenges and no coordination game was observed in marital expectation \cite{EffeVogt15}.  Studies show that there may be more than one tipping point other than marriageability determining women’s fgc decision \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?} as well as that it can be a social bond for women \cite{Mack00, DuncWand11}.  Multiple theoretical frameworks were called to be incorporated to grasp a full explanation of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}

In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitude on the practice.  Besides social norms of FGC, women’s gender values and their social environment were also incorporated.

@@

Our findings suggest that the likelihood of whether a mother will have their daughters genital cut is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others:  the norm of FGC is synergistic, based on what women think about the other women in the community will like undergo the practice than what they think about this practice.  Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.  The similar results also applied to women’s view of whether FGC should be continued \cf{link}.  \cfjd{How to use the future-mother producing daughter model?}.  Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .

>>>>

\jdcmt{I've been talking with Mike and Katie about writing papers that are easy to read. You should focus on paragraph structure, particularly the first s. of each \P. I will send you a link.}

\jdcmt{This is a run-on sentence It is estimated,} based on a UNICEF global database \jdcmt{cite the database right here?} including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East. \jdcmt{Can this be a new sentence? are the 15 million also girls below 15? If so, link directly and if not, clarify} and 44 million of them are girls below age 15, with another 15 million girls at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC  is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.
\jdcmt{Need to think about how much to about terminology and how to say it} FGC is also known as female genital mutilation and female circumcision.  As adapted by Tostan \cite{Tost15}, \jdcmt{I don't understand any of this. Can you just say Tostan and others suggest cutting? Why can't this be put into the first s?} cutting is preferred over circumcision without diminishing or excusing the negative impact of the practice because it implies a degree of self-awareness and is considered less judgmental  \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

\jdcmt{Wordy: ``about eradication'' is indirect} The commonly shared position for the practice of FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}, as the United Nations has declared that FGC violating human rights, and promoted abandonment of the practice  \cite{WHO97, WHO08} \cfonly{add and update} \jdcmt{Simplify: it looks like there's been a consensus for eradication for decades.} .  The progress is hindered due to the complicated history of the \jdcmt{what does this mean? very practice} \cite{BergDeni12, Cami16}. The meanings of FGC are \jdcmt{don't understand: competitively defined by various groups from local religious community to international governmental institutes, and by linking the practice to cultural and religious identity in one end and to public health and human rights on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values and norms \jdcmt{you introduce norms soon, is it weird to use them now?} attached to FGC practice is essential to comprehend the persistence of FGC practice \cite{}.  Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is a key approach in comprehending,  intervening or eradicating the behaviour of FGC \cite{Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11, UNIC10, UNIC13} \cfonly{more cites}.
\jdcmt{Not sure what is the relation in terms of document flow between the s. above and the s. below.}

Social norm is often used to understand behavioural pattern of FGC \cfonly{more cite{BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, OdukAfol17, Youn02} (to confirm)}.  Identifying FGC norm is crucial in intervention of sustainable changes \cite{EffeVogt15, RimaLapi15} \cfonly{Bicc etc, more}.  Convention theory, a widely \jdcmt{not sure what this word means; inferred} approach in FGC research, posits that FGC is an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group coordination, \jd{s. starting to run on} and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe08}.  FGC is also viewed as social capital for inclusion within women’s social groups \cite{Shel-Wand11}.  When the norms within the communities are strong, individuals tend to self-enforce community norms \jdcmt{this seems circular; self-enforcing is the definition of norms} \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, DuncWand11, ShelWand11}. \cfonly{add \cite{Bicc15}}.

Although convention theory was \jdcmt{doesn't seem to mean anything; well deliberated and applied} and showed a \jdcmt{larger (than what?  do you just mean large?)} effect on FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges and no coordination game was observed in marital expectation \cite{EffeVogt15} \jdcmt{By anyone? Or just by them? It is hard for the reader to reconcile this statement with the previous one}.  Studies show that there may be more than one \jdcmt{you seem to be conflating determining factors with tipping points; tipping point} other than marriageability \jdcmt{more than one total? or more than one other? this is awkward} underlying women’s fgc decisions \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?} \jdcmt{run-on and hard to parse:} as well as that it can be a social bond for women \cite{Mack00, DuncWand11}.  Multiple theoretical frameworks were \jdcmt{what does this mean; called to be incorporated to grasp a full explanation} of the persistence and decline of FGC due to the heterogeneity of the population \cite{EffeVogt15, ModrLiu13} \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} applied on fgc \icte{CislHeis18, EffeVogt15, Harf06, PashPonn16, ShelHern06,}}

In this study, we consider multiple social determinants of FGC practice both at a individual and a community level to analyze how community of FGC expectation and beliefs associates with individual attitudes on the practice.  In addition to \jdcmt{hard to figure out what this means in this context, do you just mean attitudes about FGC? social norms of FGC,} we also incorporated information about women’s gender values and their \jdcmt{Can you explain this? social environment.}

@@

Our findings suggest that the likelihood of whether a mother will have their daughters genital cut is overdetermined by her community’s overall likelihood of mothers’ intention of cutting their daughters, fgc prevalence, among others:  the norm of FGC is synergistic, based on what women think about the other women in the community will like undergo the practice than what they think about this practice.  Our findings show that omen’s decision on cutting their daughters was clearly related to their own FGC status, personal beliefs of FGC benefits and theFGC prevalent in their community \cf{link}; yet group beliefs of FGC benefits in their community did not play a clear role in determining whether a daughter would be cut.  The similar results also applied to women’s view of whether FGC should be continued \cf{link}.  \cfjdcmt{How to use the future-mother producing daughter model?}.  Our findings suggest that FGC practice is a social norm in respect of how an individual behavioral intention on FGC is in line with how their community implement this ritual; the social norm is based on what an agent perceives what their community members think and that perception can be based on the members’ behavioural outcome (i.e., whether others had FGC) or communication about the ritual practice \cite{} .
